---
title: "CollaborativeFilteringCaculation"
author: "Jean-Francois Chartier"
date: "19 décembre 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#install packages
```{r}
if ("quanteda" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(quanteda)
if ("reshape2" %in% installed.packages()==FALSE){
  install.packages('reshape2',dependencies = TRUE)
}
library(reshape2)
if ("stringr" %in% installed.packages()==FALSE){
  install.packages('stringr',dependencies = TRUE)
}
library(stringr)
library(xml2)
if ("magrittr" %in% installed.packages()==FALSE){
  install.packages('magrittr',dependencies = TRUE)
}
library(magrittr)
if ("topicmodels" %in% installed.packages()==FALSE){
  install.packages('topicmodels',dependencies = TRUE)
}
library(topicmodels)
if ("future.apply" %in% installed.packages()==FALSE){
  install.packages('future.apply',dependencies = TRUE)
}
library(future.apply)
if ("data.table" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(data.table)

```


#Load data
```{r}
centralityAuthors.T=readRDS("centralityAuthors.rds")
posteriorTopicsForAuthors.T=readRDS("posteriorTopicsForAuthors.rds")
relationsBetweenAuthors.T=readRDS("relationsBetweenAuthors.rds")
trainTopicModelNyTimes.T=readRDS("trainTopicModelNyTimes.rds")
authorFrequency.T=readRDS("authorFrequency.rds")
myNyTimeTrainingMatrix=readRDS("myNyTimeTrainningMatrix.rds")
```

#Filter self-relation
```{r}
selfRelations=relationsBetweenAuthors.T[,1]==relationsBetweenAuthors.T[,2]
relationsBetweenAuthors.noSelf=relationsBetweenAuthors.T[selfRelations==F,]
```


#Select K strongest relations
```{r}
plan(multiprocess, workers = 7)
options(future.globals.maxSize= 996147200)
k=10
relationsTable <- as.data.table(relationsBetweenAuthors.noSelf)
meltRelationsTable=data.table::melt(relationsTable,1:2, variable.name="relation")
relationType=unique(meltRelationsTable$relation)
future.apply::future_lapply(unique(relationsTable$idAuthor.1), FUN = function(author_i){
  #author_i=98
  lapply(relationType, function(rel){
    current=meltRelationsTable[idAuthor.1==author_i & relation==rel]
    current[order(current$value, decreasing = T)[1:k]]
    })%>%rbindlist(.)
})%>%rbindlist(.)->topKRelationsTable
saveRDS(topKRelationsTable, file = "topKRelationsTable.rds")

```


#select k most important central agents
```{r}
#set how many agent to keep
k=10
centralitysTable <- as.data.table(centralityAuthors.T)
meltCentralityTable=data.table::melt(centralitysTable,1, variable.name="centrality.type")
#add key for further super fast subsetting
setkey(meltCentralityTable, centrality.type, value)
centralityType=unique(meltCentralityTable$centrality.type)
uniqueAuthors=unique(meltCentralityTable$idAuthor)

lapply(centralityType, function(rel){
  #rel="degree.centrality"
  #subset
  topKid=meltCentralityTable[.(rel),]%>%tail(., k+1)
  lapply(uniqueAuthors, function(idA){
    #find self 
    selfRelations=topKid$idAuthor==idA
    #filter self
    centralityAuthors.noSelf=topKid[selfRelations==F,]
    #keep top k
    centralityAuthors.noSelf=tail(centralityAuthors.noSelf, k)
    data.table(idAuthor.1=rep(idA, k), idAuthor.2=centralityAuthors.noSelf$idAuthor, relation=centralityAuthors.noSelf$centrality.type, value=centralityAuthors.noSelf$value)
  })%>%rbindlist(.)
  
})%>%rbindlist(.)->topKCentralityTable

saveRDS(topKCentralityTable, file = "topKCentralityTable.rds")


```



#compute CF from k most strongest relations 

```{r}
topKRelationsTable=readRDS("topKRelationsTable.rds")
topKCentralityTable=readRDS("topKCentralityTable.rds")

#concat
topKRelationsTable=rbind(topKRelationsTable, topKCentralityTable)

idAuthorForTopic=rownames(posteriorTopicsForAuthors.T$topics)
lapply(unique(topKRelationsTable$idAuthor.2), function(i){
  #print(i)
  #i=2910
  #i=886
  #i=2578
  values=topKRelationsTable[idAuthor.2==i]
  
  sapply(posteriorTopicsForAuthors.T$topics[which(idAuthorForTopic==i),], function(t){
    t*values$value
  })->w
  if (is.matrix(w)==F){
    w=as.matrix(w)%>%t(.)%>%set_colnames(.,posteriorTopicsForAuthors.T$topics%>%colnames(.))
  } else{
    w=w%>%set_colnames(.,posteriorTopicsForAuthors.T$topics%>%colnames(.))
    }
  #w$topic.value=t
  values=cbind(values, w)%>%melt(., id.vars=(1:4), variable.name="topic", value.name="topic.value")
  
})%>%rbindlist(.)->meltedResults

saveRDS(meltedResults, "cf.melted.results.rds")

```


#Averaging topic.value by authors by type of relations
```{r}
predictions=dcast(meltedResults, idAuthor.1+relation ~ topic, fun.aggregate=mean, value.var = 'topic.value')
saveRDS(predictions, file = "predictionsByRelationByTopic.rds")
```

#Collect Averaged CF results
select only authors present in the test set 
```{r}
predictions=readRDS("predictionsByRelationByTopic.rds")
posteriorForAuthorsTest=readRDS("posteriorTopicsForAuthorsTest-2019-01-04.rds")

topic.predictions=melt(predictions, id.vars=(1:2), variable.name="topic", value.name="predic.topic.value")
setkey(topic.predictions, idAuthor.1, topic)

idAuthors.train=rownames(posteriorTopicsForAuthors.T$topics)
idAuthors.test=rownames(posteriorForAuthorsTest$topics)
#keep only author present in the prediction
idAuthors.test=intersect(idAuthors.test,topic.predictions$idAuthor.1%>%unique(.))

  
lapply(1:ncol(posteriorForAuthorsTest$topics), function(topic_j){
  #topic_j=100
  
  #select only authors from test set
  lapply(idAuthors.test, function(idAuthor_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[which(idAuthors.train==idAuthor_i), topic_j]
    u=posteriorForAuthorsTest$topics[which(idAuthors.test==idAuthor_i), topic_j]
    #get idAuthor
    #idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    ij$future.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
saveRDS(finalResultsFromCF, "topic.predictions.20190106.rds")

```

#Collect Averaged CF results
select all authors from train set 
```{r}
predictions=readRDS("predictionsByRelationByTopic.rds")
#posteriorForAuthorsTest=readRDS("posteriorTopicsForAuthorsTest-2019-01-04.rds")

topic.predictions=melt(predictions, id.vars=(1:2), variable.name="topic", value.name="predic.topic.value")
setkey(topic.predictions, idAuthor.1, topic)

lapply(1:ncol(posteriorTopicsForAuthors.T$topics), function(topic_j){
  #topic_j=100
  idAuthors.train=rownames(posteriorTopicsForAuthors.T$topics)
  
  #select all authors from train set
  lapply(idAuthors.train, function(idAuthor_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[which(idAuthors.train==idAuthor_i), topic_j]
    
    #v=posteriorTopicsForAuthors.T$topics[author_i, topic_j]
    #u=posteriorForAuthorsTest$topics[author_i, topic_j]
    #get idAuthor
    #idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    #ij$future.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
saveRDS(finalResultsFromCF, "topic.predictions.for.authors.in.trainset.20190106.rds")

```

#Collect non-averaged CF results
select all authors from train set 
replace idAuthor.2 by k1,k2...k10. 
The idea here is to replace the summation function of CF by a learner
```{r}
meltedResults=readRDS("cf.melted.results.rds")
#sort
setkey(meltedResults, idAuthor.1, relation, topic, value)
#replace idAuthor.2 by k1,k2...k10
k=10
rankId=lapply(1:k, function(x){
  abs(x-k)+1
})
#replicate rank for all relationType (7) and topics (200)
nRelType=meltedResults$relation%>%unique(.)%>%length(.)
nTopics=meltedResults$topic%>%unique(.)%>%length(.)
rankId=rep(rankId, (nRelType*nTopics))%>%unlist(.)

lapply(meltedResults$idAuthor.1%>%unique(.), function(id1_i){
  #id1_i="292"
  id1=meltedResults[.(id1_i),]
  id1$rank=rankId
  id1
})%>%rbindlist(.)->meltedResultsWithRank

topic.predictions=meltedResultsWithRank
setkey(topic.predictions, idAuthor.1, topic)

lapply(1:ncol(posteriorTopicsForAuthors.T$topics), function(topic_j){
  #topic_j=100
  idAuthors.train=rownames(posteriorTopicsForAuthors.T$topics)
  
  #select all authors from train set
  lapply(idAuthors.train, function(idAuthor_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[which(idAuthors.train==idAuthor_i), topic_j]
    
    #v=posteriorTopicsForAuthors.T$topics[author_i, topic_j]
    #u=posteriorForAuthorsTest$topics[author_i, topic_j]
    #get idAuthor
    #idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    #ij$future.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
saveRDS(finalResultsFromCF, "non.averaged.topic.predictions.for.authors.in.trainset.woth.rank.20190107.rds")

```

#Collect non-averaged CF results for test set
select all authors from TEST set 
replace idAuthor.2 by k1,k2...k10. 
The idea here is to replace the summation function of CF by a learner
```{r}
#posteriorForAuthorsTest=readRDS("posteriorTopicsForAuthorsTest-2019-01-04.rds")

#read data for only the first month of 2006
posteriorForAuthorsTest=readRDS("posteriorTopicsForFirstMonthAuthorsTest-2019-01-09.rds")

meltedResults=readRDS("cf.melted.results.rds")
#sort
setkey(meltedResults, idAuthor.1, relation, topic, value)
#replace idAuthor.2 by k1,k2...k10
k=10
rankId=lapply(1:k, function(x){
  abs(x-k)+1
})
#replicate rank for all relationType (7) and topics (200)
nRelType=meltedResults$relation%>%unique(.)%>%length(.)
nTopics=meltedResults$topic%>%unique(.)%>%length(.)
rankId=rep(rankId, (nRelType*nTopics))%>%unlist(.)

lapply(meltedResults$idAuthor.1%>%unique(.), function(id1_i){
  #id1_i="292"
  id1=meltedResults[.(id1_i),]
  id1$rank=rankId
  id1
})%>%rbindlist(.)->meltedResultsWithRank

topic.predictions=meltedResultsWithRank
setkey(topic.predictions, idAuthor.1, topic)

idAuthors.train=rownames(posteriorTopicsForAuthors.T$topics)
idAuthors.test=rownames(posteriorForAuthorsTest$topics)
#keep only author present in the prediction
idAuthors.test=intersect(idAuthors.test,topic.predictions$idAuthor.1%>%unique(.))

  
lapply(1:ncol(posteriorForAuthorsTest$topics), function(topic_j){
  #topic_j=100
  
  #select only authors from test set
  lapply(idAuthors.test, function(idAuthor_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[which(idAuthors.train==idAuthor_i), topic_j]
    u=posteriorForAuthorsTest$topics[which(idAuthors.test==idAuthor_i), topic_j]
    #get idAuthor
    #idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    ij$future.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
#saveRDS(finalResultsFromCF, "non.averaged.topic.predictions.for.authors.in.testset.woth.rank.20190107.rds")

saveRDS(finalResultsFromCF, "non.averaged.topic.predictions.for.authors.in.testsetFirstMonth.with.rank.20190109.rds")

```

##Collect non-averaged CF results
select all authors from train set 
not sure how to use it
```{r}
#predictions=readRDS("predictionsByRelationByTopic.rds")
meltedResults=readRDS("cf.melted.results.rds")
#posteriorForAuthorsTest=readRDS("posteriorTopicsForAuthorsTest-2019-01-04.rds")

topic.predictions=meltedResults
setkey(topic.predictions, idAuthor.1, topic)

lapply(1:ncol(posteriorTopicsForAuthors.T$topics), function(topic_j){
  #topic_j=100
  idAuthors.train=rownames(posteriorTopicsForAuthors.T$topics)
  
  #select all authors from train set
  lapply(idAuthors.train, function(idAuthor_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[which(idAuthors.train==idAuthor_i), topic_j]
    
    #v=posteriorTopicsForAuthors.T$topics[author_i, topic_j]
    #u=posteriorForAuthorsTest$topics[author_i, topic_j]
    #get idAuthor
    #idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    #ij$future.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
saveRDS(finalResultsFromCF, "non.averaged.topic.predictions.for.authors.in.trainset.20190106.rds")

```


#Collect Averaged CF results (old)
old one without future prediction
```{r}
predictions=readRDS("predictionsByRelationByTopic.rds")
posteriorForAuthorsTest=readRDS("posteriorTopicsForAuthorsTest-2019-01-04.rds")

topic.predictions=melt(predictions, id.vars=(1:2), variable.name="topic", value.name="predic.topic.value")
setkey(topic.predictions, idAuthor.1, topic)

lapply(1:ncol(posteriorTopicsForAuthors.T$topics), function(topic_j){
  #topic_j=100
  lapply(1:nrow(posteriorTopicsForAuthors.T$topics), function(author_i){
    #topic_j=100
    #author_i=886
    v=posteriorTopicsForAuthors.T$topics[author_i, topic_j]
    u=posteriorForAuthorsTest$topics[author_i, topic_j]
    #get idAuthor
    idAuthor_i=rownames(posteriorTopicsForAuthors.T$topics)[author_i]
    idTopic_j=colnames(posteriorTopicsForAuthors.T$topics)[topic_j]
    
    ij=topic.predictions[.(idAuthor_i, idTopic_j),]
    #add past observed topic for author
    ij$past.observed.topic=rep(v, nrow(ij))
    ij$futur.observed.topic=rep(u, nrow(ij))
    ij
  })%>%rbindlist(.)
})%>%rbindlist(.)->topic.predictions

finalResultsFromCF=topic.predictions
saveRDS(finalResultsFromCF, "topic.predictions.rds")

```

