---
title: "PreproNYTime2006"
author: "Jean-Francois Chartier"
date: "6 décembre 2018"
output: 
  html_document:
    number_sections: true
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE)
```

#install packages
```{r}
if ("quanteda" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(quanteda)
if ("reshape2" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(reshape2)
if ("stringr" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(stringr)
if ("xml2" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(xml2)
if ("magrittr" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(magrittr)
if ("topicmodels" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(topicmodels)
if ("proxy" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(proxy)
if ("igraph" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(igraph)
if ("data.table" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(data.table)

```


#Get Data
##get documents
```{r}
library(xml2)
library(magrittr)
#nyXML=xml2::read_xml("dataForTest.xml", encoding="ANSI")

nyXML=xml2::read_xml("nytCorpus2003-2005LemmatiseAntidictionnaireFiltreToutSaufNomAdjectifVerbeUTF8_formatJFC.xml", encoding="ANSI")
#xml_name(nyXML)
all.docs.nodes=xml_find_all(nyXML, ".//document")

```

##get authors
all unique authors
id rows are used as id authors
```{r}
#important de concat author names
#
authorFrequency=xml2::xml_find_all(all.docs.nodes, ".//auteur")%>%xml_text(.)%>%table(.)%>%as.data.frame(., stringsAsFactors=F)%>% set_colnames(., c("author.name", "frequency")) %>%data.table::as.data.table(.)

#select only authors who wrote 2 and more articles
authorFrequency=authorFrequency[frequency>1,]
authorFrequency$idAuthor=1:length(authorFrequency$author.name)

#uniqueAuthors=authorFrequency$author.name

#old script
#uniqueAuthors=xml2::xml_find_all(all.docs.nodes, ".//auteur")%>%xml_text(.) %>%unique(.)
saveRDS(authorFrequency, "authorFrequency.rds")
```

##get id authors by document
```{r}
#paralle lapply does not work here
#library(future.apply)
#plan(multiprocess, workers = 6)

allIdAuthorsByDoc=sapply(all.docs.nodes, FUN = function(x){
  authors_i= xml2::xml_find_all(x, ".//auteur")
  if (length(authors_i)>0){
    lapply(authors_i, function(y){
      a=xml_text(y) 
      authorFrequency$idAuthor[authorFrequency$author.name==a]
    })
  }
  else{
    list()
  }
})
```
##Subset indexed document with authors
keep only doc with indexed authors. In other words, empty list (with no attributed idAutor) are filtered out
```{r}
idsT=sapply(allIdAuthorsByDoc, function(x) length(unlist(x))>0)
allIdAuthorsByDoc=allIdAuthorsByDoc[idsT]
all.docs.nodes=all.docs.nodes[idsT]
```



##get info from documents
```{r}

allSeg=lapply(all.docs.nodes, FUN = function(x){
  seg_i = x %>% xml2::xml_find_first(., ".//segment")%>%xml_text(.)
})%>%unlist(.)

allDate=lapply(all.docs.nodes, FUN = function(x){
  date_i= x %>% xml2::xml_find_first(., ".//date")%>%xml_integer(.)
})%>%unlist(.)

df.docs=data.frame(segment = allSeg, date =  allDate, stringsAsFactors = F)
df.docs$idAuthors=allIdAuthorsByDoc
```

#Preprocessing data

##cleaning corpus
```{r}
library(stringr)
# tokenisation selon quanteda
preprocesCorpus=stringr::str_replace_all(df.docs$segment,"[\r\n]" , "")
#remove all non graphical caracther
preprocesCorpus=stringr::str_replace_all(preprocesCorpus,"[^[:graph:]]", " ")
#remove whitespace
preprocesCorpus=stringr::str_trim(preprocesCorpus)
```


##Tokinization and word filtering
```{r}
library(quanteda)

preprocesCorpus=quanteda::tokens(x=preprocesCorpus,what="word", remove_punct = TRUE, remove_numbers = TRUE, remove_separators = TRUE,remove_hyphens = TRUE, remove_symbols=TRUE, remove_url = TRUE)

preprocesCorpus=quanteda::tokens_tolower(preprocesCorpus)

#myStopWords=unique(c(stopwords("en", source = "smart"), c("yes", "no", "thing", "can", "okay", "ok", "just", "good", "like", "something", "one", "moment", "say", "go", "speeches", "pages", "online", "default.aspx", "www.bankofengland.co.uk")))

myStopWords=unique(c(stopwords("en", source = "smart")))

# filtrer selon un antidictionnaire et singleton
preprocesCorpus=quanteda::tokens_remove(preprocesCorpus, case_insensitive = F, valuetype = "glob", pattern=myStopWords, min_nchar=3)

#lemmatization
#no need to lemmatize, the corpus was already lemmatized
#preprocesCorpus=sapply(preprocesCorpus, FUN = function(seg)  paste0(textstem::lemmatize_words(seg), collapse = " "))
#preprocesCorpus=quanteda::tokens(preprocesCorpus)

print(c("corpus size after preprocessing : " , length(paste(unlist(preprocesCorpus)))))

print(c("vocabulary size after preprocessing : ", length(unique(paste(unlist(preprocesCorpus))) )))

df.docs$tokens=preprocesCorpus
```


#Modeling 
##vectorization of documents
```{r ,cache=T}
#Vectorize documents 
myNyTimeMatrix = quanteda::dfm(x=df.docs$tokens, tolower=FALSE)

#set filter
minDocFreq = 20
maxDocFreq = length(myNyTimeMatrix)*.66

#filter to rare and to frequent words and ngrams 
myNyTimeMatrix<-quanteda::dfm_trim(x=myNyTimeMatrix, min_docfreq = minDocFreq, max_docfreq = maxDocFreq, docfreq_type="count")

# imprimer nombre de dimensions de la matrice
print(paste("nombre de mots differents apres filtrage base sur la frequence documentaire : ", length(myNyTimeMatrix@Dimnames$features)))

saveRDS(myNyTimeMatrix, "myNyTimeTrainningMatrix.rds")

```

##filter empty documents

```{r}
nonEmptyVectors=quanteda::rowSums(myNyTimeMatrix)>0
#old very unoptimized solution
#nonEmptyVectors2 = apply(X = as.matrix(myNyTimeMatrix), MARGIN = 1, FUN = function(x) sqrt(sum(x^2))>0)
myNyTimeMatrix=myNyTimeMatrix[nonEmptyVectors,]
df.docs=df.docs[nonEmptyVectors,]

```
##LDA based topic modeling of documents
```{r}
library(topicmodels)
burnin <- 100
iter <- 2000
thin <- 500
seed <-123 # keep fixed, to garantee reproductibility
nstart <- 1
best <- TRUE
k<-200 # number of topics

#convert quanteda format to tm format
dtm_matrix = quanteda::as.DocumentTermMatrix(myNyTimeMatrix)
#launch topic modeling
topics<-topicmodels::LDA(dtm_matrix, k, method="Gibbs", control=list(nstart=nstart, seed = seed, best=best, burnin = burnin, iter = iter, thin=thin))

```

##save topic model
```{r}
saveRDS(topics, "trainTopicModelNyTimes.rds")
```


#Journalists' semantic preferences

##filter out document wihout author
```{r}
numberAuthors=sapply(df.docs$idAuthors, FUN = function(x) length(x))
df.docs=df.docs[numberAuthors>0,]
```

##aggregate to journalist*word matrix
```{r}

docAuthorAdjencency = quanteda::dfm(x=df.docs$idAuthors %>% as.tokens(.), tolower=FALSE)

authorWordTFMatrix=matrix(nrow = ncol(docAuthorAdjencency), ncol = ncol(myNyTimeMatrix))
#rownames are id authors 
# important here to select from docAuthorAdjencency, because after filtering empty segment, we have authors in the corpus who are never instanciated in the matrix 
rownames(authorWordTFMatrix)=colnames(docAuthorAdjencency)
for (j in 1: ncol(docAuthorAdjencency)){
  idDocs=which((docAuthorAdjencency)[,j]%>%as.matrix(.)>0)
  myNyTimeMatrix[idDocs,] %>% colSums(.)->authorWordTFMatrix[j,]
}

```

##Topic a posteriori of journalists
```{r}
posteriorForAuthors=topicmodels::posterior(topics, newdata = authorWordTFMatrix)
saveRDS(posteriorForAuthors, "posteriorTopicsForAuthors.rds")
```


#Compute relation between journalist

## get author cooccurrence matrix
the number of time 2 authors co-wrote an article
```{r}
authorAuthorMatrix=(t(docAuthorAdjencency)) %*% docAuthorAdjencency

#to retrive relation between 2 authors you need to used @dimnames
#which(authorAuthorMatrix@Dimnames[[1]]==1)

authorCoSignature=as.matrix(authorAuthorMatrix)%>%reshape2::melt(., value.name="co.writting.frequency")

```

##semantic similarity relation between authors
```{r}
library(proxy)

authorByAuthorSemSim=proxy::simil(authorWordTFMatrix, by_rows = T, method = "cosine")%>%as.matrix(.)%>%reshape2::melt(., value.name="semantic.similarity")

```


## social structural equivalence
```{r}
authorByAuthorSocialEqui=proxy::simil(as.matrix(authorAuthorMatrix), by_rows = T, method = "cosine")%>%as.matrix(.)%>%reshape2::melt(., value.name="structural.equivalence")
```

##Build igraph structure
```{r}
library(igraph)
#library(network)
#library(intergraph) # used to encode object from one igraph to network

graphOFAuthors= igraph::graph_from_adjacency_matrix(authorAuthorMatrix, mode = "undirected", diag = F)
```


## get social proximity relation
define social proximity betwwen 2 nodes as the shortest path divided by the graph diameter
```{r}

distBetweenAuthors=distances(graph = graphOFAuthors)

#because the minimal possible distance is 1, we obtain a normalized proximity by 1/geodesic.length
socialProxAuthor=1/distBetweenAuthors
#replace the diagonal with 0, 
socialProxAuthor[is.infinite(socialProxAuthor)]=0
socialProxAuthor=socialProxAuthor%>%reshape2::melt(., value.name="social.proximity")
#plot(graphOFAuthors)
```

##get assortativity
not sure if relevant. The hypothesis here is that agents with similair degree (>0) in a network should influence eauch other more than people with different positions  
```{r}

```


##save relation dataframe
```{r}

colnames(socialProxAuthor)=c("idAuthor.1", "idAuthor.2", names(socialProxAuthor)[3])


relationsBetweenAuthors=cbind(socialProxAuthor, structural.equivalence=authorByAuthorSocialEqui$structural.equivalence, semantic.similarity=authorByAuthorSemSim$semantic.similarity, co.writting.frequency=authorCoSignature$co.writting.frequency)

saveRDS(relationsBetweenAuthors, "relationsBetweenAuthors.rds")
```


#Compute centralities

##Degree centrality
```{r}
#degreeCentrality=authorAuthorMatrix%>%rowMeans()
#names(degreeCentrality)=authorAuthorMatrix@Dimnames[[1]]

#use igraph function for consistency
degreeCentrality=degree(graphOFAuthors, mode = "all", normalized = T)

```

##Closeness centrality
as the mean of social proximities
```{r}
# noes not work because the graph is disconnected. Use instead rowmeans from proximity matrix
#closeCentrality=closeness(graphOFAuthors, mode = "all")

#be sure that socialProxAuthor has no infinite values
proxA=(1/distBetweenAuthors)
proxA[is.infinite(proxA)]=0

closeCentrality=rowMeans(proxA)

```

## betweenness centrality
```{r}
betweennessCentrality=betweenness(graphOFAuthors, directed = F, normalized = T)
```

##save centrality df
```{r}
n=nrow(authorAuthorMatrix)
centralityAuthors= data.frame(idAuthor=names(degreeCentrality), degree.centrality=degreeCentrality, closeness.centrality=closeCentrality, betweenness.centrality=betweennessCentrality)

saveRDS(centralityAuthors, "centralityAuthors.rds")
```

#Save Corpus Info Data Frame
```{r}
saveRDS(df.docs, "nyTimeCorpusInfoDataFrame-2018-12-10.rds")
```

#END

